MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-04-20 latex/paper/paper.tex
carry chains

        Shown in Figure \ref{fig:intersite_intrasite} are two possible placements for this cell net. 
        On the right, the cells are placed across different Sites, thus the only way to route the net between the cells is through general inter-site routing. 
        On the bottom left, the cells are placed within the same Site, taking advantage of the intra-site routing and avoiding costly inter-site routing.

@@

    \textbf{CARRY} \quad
        An FPGA design will also typically implement many adders, counters, subtractors, or comparators, all of which are based on binary addition. 
        They are so ubiquitous that every that in the 7-Series architecture, every SLICE features a \emph{CARRY4} BEL -- a 4-bit carry-lookahead (CLA) adder. 
        These CARRY4 blocks can be chained vertically across SLICEs for implementing wide adders efficiently.

>>>>

        Shown in Figure \ref{fig:intersite_intrasite} are two possible placements for a LUT-FF Pair on the physical device. 
        On the right, the cells are placed across different Sites, thus the only way to route the net between the cells is through general inter-site routing. 
        On the bottom left, the cells are placed within the same Site in the same lane, taking advantage of the intra-site routing without burdening the general router with additional inter-site routing. 
        This is an important consideration for minimizing wirelength during placement.

@@

    \textbf{CARRY} \quad
        An FPGA design will also typically implement many adders, counters, subtractors, or comparators, all of which are based on binary addition. 
        They are so ubiquitous that every that in the 7-Series architecture, every SLICE features a \emph{CARRY4} BEL -- a 4-bit carry-lookahead (CLA) adder. 
        These CARRY4 blocks can be chained vertically across SLICEs for implementing wide adders efficiently. 
        These CARRY4 BELs will also be connected to LUTs and FFs, and should be placed in the same Site whenever possible to minimize wirelength. 
        \begin{figure*}[]
            \centering
            \includegraphics[width=16.0cm]{figures/carry_chain_edif_3.png}
            \caption{A carry chain of size 3 as shown in the Vivado EDIF netlist viewer}
            \label{fig:carry_chain_edif}
        \end{figure*}
